### 2016-07-02 docs/ms_communitySynchrony.tex
final edits for ELE resubmission

\usepackage{lineno}
\linenumbers
\usepackage{setspace}
\usepackage{todonotes}
\doublespacing
\usepackage{color}
\usepackage{rotating}

@@

\begin{abstract}
Temporal asynchrony among species is an important mechanism through which diversity can stabilize ecosystem functioning, but identifying the mechanisms that determine synchrony remains a challenge.
Here, we refine and test theory showing that synchrony depends on three factors: species responses to environmental variation, interspecific competition, and demographic stochasticity. We then conduct simulation experiments with empirical population models to quantify the relative importance of these factors in five plant communities.
Simulation experiments showed that the average synchrony of per capita growth rates, which can range from 0 (perfect asynchrony) to 1 (perfect synchrony), was higher when environmental variation was present (0.62) rather than absent (0.43).
Removing interspecific competition and demographic stochasticity had small effects on synchrony. In these plant communities, where species interactions and demographic stochasticity have little influence, synchrony reflects the covariance in species responses to the environment.
\end{abstract}

@@

Ecosystems are being transformed by species extinctions (Cardinale et
al. 2012), changes in community composition (Vellend et al. 2013,
Dornelas et al. 2014), and anthropogenic environmental change (Vitousek
et al. 1997), impacting the provisioning and stability of ecosystem
services (Loreau et al. 2001, Hooper et al. 2005, Rockstrom et al.
2009). Experiments have provided compelling evidence that decreases in
species richness will decrease productivity (Tilman et al. 2001) and the
temporal stability of productivity (Tilman et al. 2006, Hector et al.
2010). The stabilizing effect of species richness stems from individual
species responding to environmental fluctuations (environmental
stochasticity), or fluctuating asynchronously because of random chance
events (demographic stochasticity). (Isbell et al. 2009, Hector et al.
2010, {{de Mazancourt}} et al. 2013). Species richness affects synchrony
because larger species pools are more likely to contain species that
respond disimilarly to environmental conditions (Yachi and Loreau 1999),
implying that species losses will reduce ecosystem stability. Even
without species losses, abiotic homogenization can weaken compensatory
dynamics and, in turn, decrease temporal stability of ecosystem
functioning (Hautier et al. 2014). Predicting the impacts of global
change requires a mechanistic understanding of species synchrony in
natural settings.

Theory identifies the three main determinants of species synchrony as
environmental stochasticity, demographic stochasticity, and
interspecific competition (Loreau and {{de Mazancourt}} 2008, 2013,
Gonzalez and Loreau 2009). For example, in a community composed of large
(no demographic stochasticity) and weakly interacting (no interspecific
competition) populations, community-wide species synchrony should be
determined by the covariance of species' responses to the environment
(Loreau and {{de Mazancourt}} 2008). However, such a prediction relies
on a relatively simple population model and only holds under two
assumptions: (i) species' responses to the environment are similar in
magnitude and (ii) all species have similar growth rates. Whether such
theoretical predictions hold in natural communities where species
differences are unlikely to be symmetrical remains unkown: no study has
explicitly tested theory on the drivers of species synchrony in natural
communities.

In grasslands, most empirical studies have focused on whether species
synchrony is primarily an outcome of species-specific responses to
environmental conditions (Hautier et al. 2014) or competition (Gross et
al. 2014). Even beyond grassland studies, whether competition or
environmental responses drive compensatory dynamics remains
controversial (reviewed in Gonzalez and Loreau 2009). In part,
controversy remains because quantifying the relative strengths of each
driver on the degree of synchrony from community time series (e.g.,
Houlahan et al. 2007) is impossible. This is because an unbiased null
expectation for synchrony does not exist (Loreau and {{de Mazancourt}}
2008) and observed synchrony can arise from non-unique combinations of
factors (Ranta et al. 2008). For example, weak synchrony of population
abundances could reflect positive environmental correlations
(synchronizing effect) offset by strong competition (desynchronizing
effect), or negative environmental correlations and weak competition.

The best way to quantify the effects of environmental stochasticity,
demographic stochasticity, and interspecific competition is to remove
them one-by-one, and in combination. In principle, this could be done in
an extremely controlled laboratory setting, but empirically-based models
of interacting populations, fit with data sets from natural communities,
offer a practical alternative. For example, Mutshinda et al. (2009) fit
a dynamic population model to several community time series of insect
and bird abundances. They used a statistical technique to decompose
temporal variation into competition and environmental components, and
found that postively correlated environmental responses among species
determined community dynamics. While a major step forward, Mutshinda et
al.'s (2009) modeling technique relied on abundance data that may or may
not reliably capture competitive interactions that occur at the
individual level. Furthermore, although Mutshinda et al. (2009)
quantified the relative importance of environmental stochasticity and
competition to explain the observed variation of species synchrony, they
did not use the model to quantify how much synchrony would change when
each factor is removed.

Here, we use multi-species population models fit to long-term
demographic data from five semi-arid plant communities to test theory on
the drivers of species synchrony. Our objectives are to (1) derive and
test theoretical predictions of species synchrony and (2) determine the
relative influence of environmental stochasticity, demographic
stochasticity, and interspecific competition on species synchrony in
natural plant communities. To achieve these objectives, we first refine
theory that has been used to predict the effects of species richness on
ecosystem stability ({{de Mazancourt}} et al. 2013) and species
synchrony (Loreau and {{de Mazancourt}} 2008) to generate predictions of
community-wide species synchrony under two limiting cases derived from
the dynamics of individual species in monoculture. We then confront our
theoretical predictions with simulations from the empirically-based
population models. Second, we use the multi-species population models to
perform simulation experiments that isolate the effects of environmental
stochasticity, demographic stochasticity, and interspecific competition
on community-wide species synchrony. Given that our population models
capture the essential features of community dynamics important to
synchrony (density-dependence, and demographic and environmental
stochasticity), and that these models successfully reproduce observed
community dynamics (Chu and Adler 2015), perturbing the models can
reveal the processes that determine species synchrony in our focal
grassland communities.

@@

While existing theory has identified the factors driving synchrony, we
do not have a simple expression to predict synchrony in a particular
community with all factors operating simultaneously. However, we can
derive analytical predictions for species synchrony under special
limiting cases. We focus on synchrony of per capita growth rates, rather
than abundances, because growth rates represent the instantaneous
response of species to the environment and competition, and are less
susceptible to the legacy effects of drift and disturbance (Loreau and
{{de Mazancourt}} 2008). We present equivalent results for synchrony of
species abundances in the Online Supporting Information, and show that
they lead to the same overall conclusions as synchrony of per capita
growth rates. Following Loreau and {{de Mazancourt}} (2008) and {{de
Mazancourt}} et al. (2013), we define population growth, ignoring
observation error, as

@@

\noindent where \(N_i(t)\) is the biomass of species \emph{i} in year
\emph{t}, and \(r_i(t)\) is its population growth rate in year \emph{t}.
\(r_{mi}\) is species \emph{i}'s intrinsic rate of increase, \(K_i\) is
its carrying capacity, and \(\alpha_{ij}\) is the interspecific
competition coefficient representing the effect of species \emph{j} on
species \emph{i}. Environmental stochasticity is incorporated as
\(\sigma_{ei}u_{ei}(t)\), where \(\sigma_{ei}^2\) is the environmental
variance and \(u_{ei}\) are normal random variables with zero mean and
unit variance that are independent through time but may be correlated
between species. Demographic stochasticity arises from variations in
births and deaths among individuals (e.g., same states, different
fates), and is included in the model as a first-order, normal
approximation (Lande et al. 2003, {{de Mazancourt}} et al. 2013).
\(\sigma_{di}^2\) is the demographic variance and \(u_{di}(t)\) are
independent normal variables with zero mean and unit variance. To derive
analytical predictions we solved a first-order approximation of Equation
2 ({{de Mazancourt}} et al. 2013 and Online Supporting Information).

@@

Our first prediction assumes no interspecific interactions, no
environmental stochasticity, identical intrinsic growth rates, and that
demographic stochasticity is operating but all species have identical
demographic variances. This limiting case, \(\mathcal{M}_{D}\),
represents a community where dynamics are driven by demographic
stochasticity alone. Our prediction is

\begin{equation}
\phi_{R,\mathcal{M}_{D}} = \frac{\sum_i p_i^{-1}}{\left(\sum_i p_i^{-1/2} \right)^2}
\end{equation}

\noindent for synchrony of per capita growth rates. \(p_i\) is the
average frequency of species \emph{i}, \(p_i = N_i/N_T\). When all
species have identical abundances and \(p_i = 1/S\), where \emph{S} is
species richness, synchrony equal 1/S (Loreau and {{de Mazancourt}}
2008).

Our second limiting case assumes only environmental stochasticity is
operating. Thus, there are no interspecific interactions, demographic
stochasticity is absent, intrinsic growth rates are identical, and
environmental variance is identical for all species. Our prediction for
this limiting case, \(\mathcal{M}_{E}\), is

\begin{equation}
\phi_{R,\mathcal{M}_{E}} = \frac{\sum_{i,j}\text{cov}(u_{ei},u_{ej})}{S^2}
\end{equation}

\noindent{} for synchrony of per capita growth rates, where
\(\text{cov}(u_{ei},u_{ej})\) is the standardized covariance of
environmental responses between species \emph{i} and species \emph{j}.
Confronting our theoretical predictions with data requires estimates of
species dynamics of large populations (no demographic stochasticity) in
monoculture (no interspecific interactions) to calculate the covariance
of species' environmental responses. To estimate environmental responses
in natural communities, we turn to our population models built using
long-term demographic data.

@@

In the early 20th century, several range experiment stations in the
western U.S. began mapping permanent quadrats, and conducted annual
censuses for decades. We use such long-term demographic data sets from
five semiarid grasslands in the western United States (described in
detail by Chu and Adler 2015). Each study site includes a set of
1-\(\text{m}^2\) permanent quadrats within which all individual plants
were identified and mapped annually using a pantograph (Hill 1920). The
resulting mapped polygons represent basal cover for grasses and canopy
cover for shrubs. Data come from the Sonoran desert in Arizona (Anderson
et al. 2012), sagebrush steppe in Idaho (Zachmann et al. 2010), southern
mixed prairie in Kansas (Adler et al. 2007), northern mixed prairie in
Montana (Anderson et al. 2011), and Chihuahuan desert in New Mexico
(Anderson et al. in preparation, Chu and Adler 2015) (Table 1).

@@

\noindent where \(\sigma_{r_{i}}\) is the temporal variance of species
\emph{i}`s per capita population growth rate (\(r_i\)) and
\(\sigma^{2}_{T}\) is the temporal variance of the aggregate
community-level growth rate. \(\phi\) ranges from 0 at perfect
asynchrony to 1 at perfect synchrony (Loreau and {{de Mazancourt}}
2008). We use the same equation to calculate observed synchrony of
species' percent cover, which we present to relate our results to
previous findings, even though we focus on synchrony of growth rates in
our model simulations (see below).

@@

Vital rate regressions are the building blocks of our dynamic models: an
integral projection model (IPM) and an individual-based model (IBM). We
followed the approach of Chu and Adler (2015) to fit statistical models
for survival, growth, and recruitment (see Online Supporting Information
for full details). We modeled survival probability of each genet as
function of genet size, temporal variation among years, permanent
spatial variation among groups of quadrats, and local neighborhood
crowding from conspecific and heterospecific genets. Regression
coefficients for the effect of crowding by each species can be
considered a matrix of interaction coefficients whose diagonals
represent intraspecific interactions and whose off-diagonals represent
interspecific interactions (Adler et al. 2010). These interaction
coefficients can take positive (facilitative) or negative (competitive)
values. We modeled growth as the change in size of a genet from one year
to the next, which depends on the same factors as the survival model. We
fit the survival and growth regressions using INLA (Rue et al. 2014), a
statistical package for fitting generalized linear mixed effects models
via approximate Bayesian inference (Rue et al. 2009), in R (R Core Team
2013). Genet size and crowding were treated as fixed effects; spatial
(quadrat groupings) variation was treated as a random effect on the
intercept and temporal (interannual) variation was treated as random
effects on the intercept and the effect of genet size in the previous
year (Online Supporting Information).

We modeled recruitment at the quadrat scale, rather than the individual
scale, because it is impossible to attribute new genets to specific
parents (Chu and Adler 2015). Our recruitment model assumes that the
number of recruits produced in each year follows a negative binomial
distribution with the mean dependent on the cover of the parent species,
permanent spatial variation among groups, temporal variation among
years, and inter- and intraspecific interactions as a function of total
species' cover in the quadrat. We fit the recruitment model using a
hierarchical Bayesian approach implemented in JAGS (Plummer 2003) using
the `rjags' package (Plummer 2014) in R. Again, temporal and spatial
variation were treated as random effects.

@@

We performed removal simulation experiments where drivers (environmental
stochasticity, demographic stochasticity, or interspecific competition)
were removed one-by-one and in combination. To remove interspecific
interactions, we set the off-diagonals of the interaction matrix for
each vital rate regression to zero. This retains intraspecific
interactions, and thus density-dependence, and results in simulations
where species are effectively growing in monoculture. To remove the
effect of a fluctuating environment, we removed the temporal
(interannual) random effects from the regression equations. To remove
the effect of demographic stochasticity, we use the IPM rather than the
IBM because the IPM does not include demographic stochasticity
(demographic stochasticity cannot be removed from the IBM). Since the
effect of demographic stochasticity on population dynamics depends on
population size (Lande et al. 2003), we can control the strength of
demographic stochasticity by simulating the IBM on areas (e.g.~plots) of
different size. Indeed, results from an IBM with infinite population
size would converge on results from the IPM. Given computational
constraints, the largest landscape we simulate is a 25 \(\text{m}^2\)
plot.

We conducted the following six simulation experiments: (1) IBM: All
drivers (environmental stochasticity, demographic stochasticity, or
interspecific competition) present; (2) IPM: Demographic stochasticity
removed; (3) IBM: Environmental stochasticity removed; (4) IBM:
Interspecific competition removed; (5) IPM: Interspecific competition
and demographic stochasticity removed; (6) IBM: Interspecific
competition and environmental stochasticity removed. We ran IPM
simulations for 2,000 time steps, after an initial 500 iteration burn-in
period. This allowed species time to reach their stable size
distribution. We then calculated the synchrony of species' per capita
growth rates over 100 randomly selected contiguous 50 time-step
sections. We ran IBM simulations for 100 time steps, and repeated the
simulations 100 times for each simulation experiment. From those, we
retained only the simulations in which no species went extinct due to
demographic stochasticity. Synchrony was calculated over the 100 time
steps for each no extinction run within a model experiment. To explore
the effect of demographic stochasticity in different sized populations,
we ran simulations (1) and (6) on plot sizes of 1, 4, 9, 16, and 25
\(\text{m}^2\). All other IBM simulations were run on a 25
\(\text{m}^2\) landscape.

Results from our simulation experiments also allow us to test our
theoretical predictions. First, in the absence of interspecific
competition and demographic stochasticity, species are effectively
growing in large monocultures. Therefore, we can use results from
simulation (5) to estimate the covariance of species' responses to the
environment (\(\text{cov}(u_{ie}, u_{je})\)) and parameterize Equation
3. Parameterizing Equation 2 does not require simulation output because
the only parameters are the species' relative abundances. Second,
simulations (5) and (6) represent the simulated version of our limiting
case theoretical predictions. Thus, we directly test the theoretical
predictions by comparing them to observed synchrony and simulated
synchrony.

@@

Synchrony of species' per capita growth rates at our study sites ranged
from 0.36 to 0.89 and synchrony of percent cover ranged from 0.15 to
0.92 (Table 2). Synchrony tended to be higher in communities with few
species (Arizona and New Mexico) and/or with relatively high temporal
variability in percent cover (e.g., Montana). Synchrony was lowest in
Idaho, the only data set that includes two life forms: a shrub and three
perennial grasses (Table 1). For all five communities, species synchrony
from IPM and IBM simulations closely approximated observed synchrony
(Fig. S1). IBM-simulated synchrony is consistently, but only slightly,
lower than IPM-simulated synchrony (Fig. S1), likely due to the
desynchronizing effect of demographic stochasticity.

@@

Simulation experiments revealed that removing environmental fluctuations
has the largest impact on synchrony, leading to a reduction in synchrony
of species growth rates in four out of five communities (Fig. 1).
Removing environmental fluctuations (``No E.S'' simulations) decreased
synchrony by 33\% in Arizona, 48\% in Kansas, 39\% in Montana, and 40\%
in New Mexico. Only in Idaho did removing environmental fluctuations
cause an increase in synchrony (Fig. 1), but the effect was small (9\%
increase; Table S2). Overall, species' temporal random effects in the
statistical vital rate models are positively correlated (Table S3).
Species interactions are weak in these communities (Table S4 and Chu and
Adler 2015), and removing interspecific competition had little effect on
synchrony (Fig. 1; ``No Comp.'' simulations). Removing competition
caused, at most, a 5\% change in synchrony (Fig. 1). Removing
demographic stochasticity (``No D.S.'' simulations) caused synchrony to
increase slightly in all communities (Fig. 1), with an average 6\%
increase over synchrony from IBM simulations on a five meter area.

@@

>>>>

\usepackage{lineno}
\linenumbers
\usepackage{setspace}
\usepackage{todonotes}
\doublespacing
\usepackage{rotating}
\usepackage{color, soul}

@@

\begin{abstract}
Temporal asynchrony among species \textcolor{blue}{helps} diversity \textcolor{blue}{to} stabilize ecosystem functioning, but identifying the mechanisms that determine synchrony remains a challenge.
Here, we refine and test theory showing that synchrony depends on three factors: species responses to environmental variation, interspecific \textcolor{blue}{interactions}, and demographic stochasticity. We then conduct simulation experiments with empirical population models to quantify the relative importance of these factors in five plant communities.
\textcolor{blue}{We found} that the average synchrony of per capita growth rates, which can range from 0 (perfect asynchrony) to 1 (perfect synchrony), was higher when environmental variation was present (0.62) rather than absent (0.43).
Removing interspecific \textcolor{blue}{interactions} and demographic stochasticity had small effects on synchrony. In these plant communities, where species interactions and demographic stochasticity have little influence, synchrony reflects the covariance in species responses to the environment.
\end{abstract}

@@

Ecosystems are being transformed by species extinctions (Cardinale et
al. 2012), changes in community composition (Vellend et al. 2013,
Dornelas et al. 2014), and anthropogenic environmental change (Vitousek
et al. 1997), impacting the provisioning and stability of ecosystem
services (Loreau et al. 2001, Hooper et al. 2005, Rockstrom et al.
2009). Experiments have provided compelling evidence that decreases in
species richness will decrease productivity (Tilman et al. 2001) and the
temporal stability of productivity (Tilman et al. 2006, Hector et al.
2010). The stabilizing effect of species richness stems from individual
species responding \textcolor{blue}{in different ways} to environmental
fluctuations (environmental stochasticity), or fluctuating
asynchronously because of random chance events (demographic
stochasticity) (Isbell et al. 2009, Hector et al. 2010, {{de
Mazancourt}} et al. 2013). Species richness affects synchrony because
larger species pools are more likely to contain species that respond
disimilarly to environmental conditions (Yachi and Loreau 1999),
implying that species losses will reduce ecosystem stability. Even
without species losses, abiotic homogenization can weaken compensatory
dynamics and, in turn, decrease temporal stability of ecosystem
functioning (Hautier et al. 2014).
\textcolor{blue}{The link between synchrony and stability means that a mechanistic understanding of synchrony can help us predict the impacts of global change on ecosystem stability.}

Theory identifies three main determinants of species synchrony:
environmental stochasticity, demographic stochasticity, and
\textcolor{blue}{interspecific interactions} (Loreau and {{de
Mazancourt}} 2008, 2013, Gonzalez and Loreau 2009). For example, in a
community composed of large \textcolor{blue}{populations} (no
demographic stochasticity)
\textcolor{blue}{with weak interspecific interations}, community-wide
species synchrony should be determined by the covariance of species'
responses to the environment (Loreau and {{de Mazancourt}} 2008).
However, \textcolor{blue}{this} prediction relies on a relatively simple
population model and only holds under two assumptions: (i) species'
responses to the environment are similar in magnitude and (ii) all
species have similar growth rates.
\textcolor{blue}{Whether such theoretical predictions hold in natural communities where species differences are unlikely to be symmetrical is unkown because few studies have explicitly tested theory on the drivers of species synchrony in natural communities}
(Mutshinda et al. 2009, Thibaut et al. 2012),
\textcolor{blue}{and they did not consider demographic stochasiticity.}

In grasslands, most empirical studies have focused on whether species
synchrony is primarily an outcome of species-specific responses to
environmental conditions (Hautier et al. 2014) or competition (Gross et
al. 2014). Even beyond grassland studies, whether competition or
environmental responses drive compensatory dynamics remains
controversial (reviewed in Gonzalez and Loreau 2009). In part,
controversy remains because quantifying the relative strengths of each
driver on the degree of synchrony from
\textcolor{blue}{the covariance matrix of species abundances} (e.g.,
Houlahan et al. 2007) is impossible. This is because an unbiased null
expectation for synchrony does not exist (Loreau and {{de Mazancourt}}
2008) and observed synchrony can arise from non-unique combinations of
factors (Ranta et al. 2008). For example, weak synchrony of population
abundances could reflect positive environmental correlations
(synchronizing effect) offset by strong competition (desynchronizing
effect), or negative environmental correlations and weak competition.

The best way to quantify the effects of environmental stochasticity,
demographic stochasticity, and interspecific
\textcolor{blue}{interactions} is to remove them one-by-one, and in
combination. In principle, this could be done in an extremely controlled
laboratory setting, but empirically-based models of interacting
populations, fit with data sets from natural communities, offer a
practical alternative. For example, Mutshinda et al. (2009) fit a
dynamic population model to several community time series of insect and
bird abundances. They used a statistical technique to decompose temporal
variation into competition and environmental components, and found that
positively correlated environmental responses among species determined
community dynamics. Thibaut et al. (2012)
\textcolor{blue}{used a similar approach for reef fish and came to a similar conclusion: environmental responses determine synchrony.}
While a major step forward, Mutshinda et al.'s (2009) and Thibaut et
al.'s (2012) modeling technique relied on abundance data that may or may
not reliably capture competitive interactions that occur at the
individual level. Furthermore, although both studies quantified the
relative importance of environmental stochasticity and
\textcolor{blue}{interspecific interactions} to explain the observed
variation of species synchrony, they did not use the model to quantify
how much synchrony would change when each factor is removed.

Here, we use multi-species population models fit to long-term
demographic data from five semi-arid plant communities to test theory on
the drivers of species synchrony. Our objectives are to (1) derive and
test theoretical predictions of species synchrony and (2) determine the
relative influence of environmental stochasticity, demographic
stochasticity, and interspecific \textcolor{blue}{interactions} on
species synchrony in natural plant communities. To achieve these
objectives, we first refine theory that has been used to predict the
effects of species richness on ecosystem stability ({{de Mazancourt}} et
al. 2013) and species synchrony (Loreau and {{de Mazancourt}} 2008) to
generate predictions of community-wide species synchrony under two
limiting cases derived from the dynamics of individual species in
monoculture. We then confront our theoretical predictions with
simulations from the empirically-based population models. Second, we use
the multi-species population models to perform simulation experiments
that isolate the effects of environmental stochasticity, demographic
stochasticity, and interspecific \textcolor{blue}{interactions} on
community-wide species synchrony. Given that our population models
capture the essential features of community dynamics important to
synchrony (density-dependence, and demographic and environmental
stochasticity), and that these models successfully reproduce observed
community dynamics (Chu and Adler 2015), perturbing the models can
reveal the processes that determine species synchrony in our focal
grassland communities.

@@

While existing theory has identified the factors driving synchrony, we
do not have a simple expression to predict synchrony in a particular
community with all factors operating simultaneously. However, we can
derive analytical predictions for species synchrony under special
limiting cases.
\textcolor{blue}{The limiting case predictions we derive serve as baselines to help us interpret results from empirically-based simulations (described below).}
We focus on synchrony of per capita growth rates, rather than
abundances, because growth rates represent the instantaneous response of
species to the environment and competition, and are less susceptible to
the legacy effects of drift and disturbance (Loreau and {{de
Mazancourt}} 2008). We present equivalent results for synchrony of
species abundances in the Online Supporting Information, and show that
they lead to the same overall conclusions as synchrony of per capita
growth rates. Following Loreau and {{de Mazancourt}} (2008) and {{de
Mazancourt}} et al. (2013), we define population growth, ignoring
observation error, as

@@

\noindent where \(N_i(t)\) is the biomass of species \emph{i} in year
\emph{t}, and \(r_i(t)\) is its population growth rate in year \emph{t}.
\(r_{mi}\) is species \emph{i}'s intrinsic rate of increase, \(K_i\) is
its carrying capacity, and \(\alpha_{ij}\) is the interspecific
competition coefficient representing the effect of species \emph{j} on
species \emph{i}. Environmental stochasticity is incorporated as
\(\sigma_{ei}u_{ei}(t)\), where \(\sigma_{ei}^2\) is the environmental
variance and \(u_{ei}\) are normal random variables with zero mean and
unit variance that are independent through time but may be correlated
between species. Demographic stochasticity arises from variations in
births and deaths among individuals (e.g., same states, different
fates), and is included in the model as a first-order, normal
approximation (Lande et al. 2003, {{de Mazancourt}} et al. 2013).
\(\sigma_{di}^2\) is the demographic variance and \(u_{di}(t)\) are
independent normal variables with zero mean and unit variance. To derive
analytical predictions we solved a first-order approximation of Equation
2 ({{de Mazancourt}} et al. 2013 and Online Supporting Information).
\textcolor{blue}{Due to the linear approximation approach, our analytical predictions will likely fail in communities where species exhibit large fluctuations due to limit cycles and chaos}
(Loreau and {{de Mazancourt}} 2008).
\textcolor{blue}{Indeed, one of the advantages of focusing on growth rates rather than abundances is that growth rates are more likely to be well-regulated around an equilibrium value, if the long-term average of a species' growth rate is relatively small}
(e.g., \(r < 2\)).

@@

Our first prediction assumes no interspecific interactions, no
environmental stochasticity, identical intrinsic growth rates, and that
demographic stochasticity is operating but all species have identical
demographic variances. This limiting case, \(\mathcal{M}_{D}\),
represents a community where dynamics are driven by demographic
stochasticity alone. Our prediction
\textcolor{blue}{for the synchrony of per capita growth rates for $\mathcal{M}_{D}$, $\phi_{R,\mathcal{M}_{D}}$, is}

\begin{equation}
\phi_{R,\mathcal{M}_{D}} = \frac{\sum_i p_i^{-1}}{\left(\sum_i p_i^{-1/2} \right)^2},
\end{equation}

\noindent where \(p_i\) is the average frequency of species \emph{i},
\(p_i = N_i/N_T\). When all species have identical abundances and
\(p_i = 1/S\), where \emph{S} is species richness, synchrony equal 1/S
(Loreau and {{de Mazancourt}} 2008).

Our second limiting case assumes only environmental stochasticity is
operating (\(\mathcal{M}_{E}\)). Thus, we assume there are no
interspecific interactions, demographic stochasticity is absent,
intrinsic growth rates are identical, and environmental variance is
identical for all species. Our prediction
\textcolor{blue}{for the synchrony of per capita growth rates for $\mathcal{M}_{E}$, $\phi_{R,\mathcal{M}_{E}}$, is }

\begin{equation}
\phi_{R,\mathcal{M}_{E}} = \frac{\sum_{i,j}\text{cov}(u_{ei},u_{ej})}{S^2},
\end{equation}

\noindent{} where \(\text{cov}(u_{ei},u_{ej})\) is the standardized
covariance of environmental responses between species \emph{i} and
species \emph{j}. Confronting our theoretical predictions with data
requires estimates of species dynamics of large populations (no
demographic stochasticity) \textcolor{blue}{growing in isolation} (no
interspecific interactions) to calculate the covariance of species'
environmental responses. To estimate environmental responses in natural
communities, we turn to our population models built using long-term
demographic data.

@@

We use long-term demographic data from five semiarid grasslands in the
western United States (described in detail by Chu and Adler 2015). Each
site includes a set of 1-\(\text{m}^2\) permanent quadrats within which
all individual plants were identified and mapped annually using a
pantograph (Hill 1920). The resulting mapped polygons represent basal
cover for grasses and canopy cover for shrubs. Data come from the
Sonoran desert in Arizona (Anderson et al. 2012), sagebrush steppe in
Idaho (Zachmann et al. 2010), southern mixed prairie in Kansas (Adler et
al. 2007), northern mixed prairie in Montana (Anderson et al. 2011), and
Chihuahuan desert in New Mexico (Anderson et al. in preparation, Chu and
Adler 2015) (Table 1).

@@

\noindent where \(\sigma_{r_{i}}\) is the temporal variance of species
\emph{i'}s per capita population growth rate (\(r_i\)) and
\(\sigma^{2}_{T}\) is the temporal variance of the aggregate
community-level growth rate. \(\phi\) ranges from 0 at perfect
asynchrony to 1 at perfect synchrony (Loreau and {{de Mazancourt}}
2008). We use the same equation to calculate observed synchrony of
species' percent cover, which we present to relate our results to
previous findings, even though we focus on synchrony of growth rates in
our model simulations (see below).

@@

Vital rate regressions are the building blocks of our dynamic models: an
integral projection model (IPM) and an individual-based model (IBM). We
followed the approach of Chu and Adler (2015) to fit statistical models
for survival, growth, and recruitment (see Online Supporting Information
for full details). We modeled survival probability of each genet as
function of genet size, temporal variation among years, permanent
spatial variation among groups of quadrats, and local neighborhood
crowding from conspecific and heterospecific genets. Regression
coefficients for the effect of crowding by each species can be
considered a matrix of interaction coefficients whose diagonals
represent intraspecific interactions and whose off-diagonals represent
interspecific interactions (Adler et al. 2010). These interaction
coefficients can take positive (facilitative) or negative (competitive)
values. We modeled growth as the change in size of a genet from one year
to the next, which depends on the same factors as the survival model. We
fit the survival and growth regressions using INLA (Rue et al. 2014), a
statistical package for fitting generalized linear mixed effects models
via approximate Bayesian inference (Rue et al. 2009), in R (R Core Team
2013).
\textcolor{blue}{Crowding was treated as a fixed effect without a temporal component because most 95\% credible intervals for random year effects on crowding broadly overlapped zero and, in a test case, including yearly crowding effects did not change our results.}
Spatial (quadrat groupings) variation was treated as a random effect on
the intercept and temporal (interannual) variation was treated as random
effects on the intercept and the effect of genet size in the previous
year (Online Supporting Information).

We modeled recruitment at the quadrat scale, rather than the individual
scale, because the original data do not attribute new genets to specific
parents (Chu and Adler 2015). Our recruitment model assumes that the
number of recruits produced in each year follows a negative binomial
distribution with the mean dependent on the cover of the parent species,
permanent spatial variation among groups, temporal variation among
years, and inter- and intraspecific interactions as a function of total
species' cover in the quadrat. We fit the recruitment model using a
hierarchical Bayesian approach implemented in JAGS (Plummer 2003) using
the `rjags' package (Plummer 2014) in R (R Core Team 2013). Again,
temporal and spatial variation were treated as random effects.

@@

We performed simulation experiments where drivers (environmental
stochasticity, demographic stochasticity, or interspecific
\textcolor{blue}{interactions}) were removed one-by-one and in
combination. To remove interspecific interactions, we set the
off-diagonals of the interaction matrix for each vital rate regression
to zero. This retains intraspecific interactions, and thus
density-dependence, and results in simulations where species are
\textcolor{blue}{growing in isolation}.
\textcolor{blue}{We cannot definitively rule out the effects of species interactions on all parameters, meaning that a true monoculture could behave differently than our simulations of a population growing without interspecific competitors.}
To remove the effect of a fluctuating environment, we removed the
temporal (interannual) random effects from the regression equations. To
remove the effect of demographic stochasticity, we use the IPM rather
than the IBM because the IPM does not include demographic stochasticity
(demographic stochasticity cannot be removed from the IBM). Since the
effect of demographic stochasticity on population dynamics depends on
population size (Lande et al. 2003), we can control the strength of
demographic stochasticity by simulating the IBM on areas (e.g.~plots) of
different size. Indeed, results from an IBM with infinite population
size would converge on results from the IPM. Given computational
constraints, the largest landscape we simulate is a 25 \(\text{m}^2\)
plot.

We conducted the following six simulation experiments: (1) IBM: All
drivers (environmental stochasticity, demographic stochasticity, or
\textcolor{blue}{interspecific interactions}) present; (2) IPM:
Demographic stochasticity removed; (3) IBM: Environmental stochasticity
removed; (4) IBM: \textcolor{blue}{Interspecific interactions} removed;
(5) IPM: \textcolor{blue}{Interspecific interactions} and demographic
stochasticity removed; (6) IBM:
\textcolor{blue}{Interspecific interactions} and environmental
stochasticity removed. We ran IPM simulations for 2,000 time steps,
after an initial 500 iteration burn-in period. This allowed species time
to reach their stable size distribution. We then calculated the
synchrony of species' per capita growth rates over 100 randomly selected
contiguous 50 time-step sections. We ran IBM simulations for 100 time
steps, and repeated the simulations 100 times for each simulation
experiment. From those, we retained only the simulations in which no
species went extinct due to demographic stochasticity. Synchrony was
calculated over the 100 time steps for each no extinction run within a
model experiment. To explore the effect of demographic stochasticity in
different sized populations, we ran simulations (1) and (6) on plot
sizes of 1, 4, 9, 16, and 25 \(\text{m}^2\). All other IBM simulations
were run on a 25 \(\text{m}^2\) landscape.

Results from our simulation experiments also allow us to test our
theoretical predictions. First, in the absence of
\textcolor{blue}{interspecific interactions} and demographic
stochasticity,
\textcolor{blue}{populations can only fluctuate in response to the environment}.
Therefore, we can use results from simulation (5) to estimate the
covariance of species' responses to the environment
(\(\text{cov}(u_{ie}, u_{je})\)) and parameterize Equation 4.
Parameterizing Equation 3 does not require simulation output because the
only parameters are the species' relative abundances. Second,
simulations (5) and (6) represent the simulated version of our limiting
case theoretical predictions. Thus, we directly test the theoretical
predictions by comparing them to observed synchrony and simulated
synchrony.

@@

Synchrony of species' per capita growth rates at our study sites range
from 0.36 to 0.89 and synchrony of percent cover ranged from 0.15 to
0.92 (Table 2). Synchrony tends to be higher in communities with few
species (Arizona and New Mexico) and/or with relatively high temporal
variability in percent cover (e.g., Montana). Synchrony is lowest in
Idaho, the only data set that includes two life forms: a shrub and three
perennial grasses (Table 1).
\textcolor{blue}{Synchrony of per capita growth rates and CV of percent cover are positively correlated}
(Pearson's \(\rho\) = 0.72). For all five communities, species synchrony
from IPM and IBM simulations closely approximated observed synchrony
(Fig. S1). IBM-simulated synchrony is consistently, but only slightly,
lower than IPM-simulated synchrony (Fig. S1), likely due to the
desynchronizing effect of demographic stochasticity.

@@

Simulation experiments revealed that removing environmental fluctuations
has the largest impact on synchrony, leading to a reduction in synchrony
of species growth rates in four out of five communities (Fig. 1).
Removing environmental fluctuations (``No E.S'' simulations) decreased
synchrony by 33\% in Arizona, 48\% in Kansas, 39\% in Montana, and 40\%
in New Mexico. Only in Idaho did removing environmental fluctuations
cause an increase in synchrony (Fig. 1), but the effect was small (9\%
increase; Table S2). Overall, species' temporal random effects in the
statistical vital rate models are positively correlated (Table S3).
Species interactions are weak in these communities (Table S4 and Chu and
Adler 2015), and removing \textcolor{blue}{interspecific interactions}
had little effect on synchrony (Fig. 1; ``No Comp.'' simulations).
Removing \textcolor{blue}{interspecific interactions} caused, at most, a
5\% change in synchrony (Fig. 1). Removing demographic stochasticity
(``No D.S.'' simulations) caused synchrony to increase slightly in all
communities (Fig. 1), with an average 6\% increase over synchrony from
IBM simulations on a 25\(\text{m}^2\) area.

@@

Gouhier, T. C., F. Guichard, and A. Gonzalez. 2010. Synchrony and
Stability of Food Webs in Metacommunities. The American Naturalist
175:E16--E34.
